Sparse Matrix Vector Multiplication with Multiple vectors and Multiple Matrices on the MIC Architecture

### 2013-10-17 code.tex
code almost ready

   //perform first tensor multiplication
   correct_vect = permute(all_vect, _MM_PERM_AAAA);
   correct_mat = _mm512_swizzle_ps(mat_ent, _MM_SWIZ_REG_AAAA);
   accu = _mm512_fmadd_ps(correct_vect, correct_mat, accu);

>>>>

   //perform first tensor multiplication
   vect = permute(all_vect, _MM_PERM_AAAA);
   mat = _mm512_swizzle_ps(mat_ent, _MM_SWIZ_REG_AAAA);
   accu = _mm512_fmadd_ps(vect, mat, accu);
